Article title

### 2017-06-27 paper-webserver.tex
ADD: updates to third para

The surveilance of bacterial pathogens is a routine function of public-health agencies. In \textit{Salmonella enterica} \cite{bell2016recent}, \textit{Escherichia coli} \cite{fratamico2016advances}, and others pathogens \cite{ronholm2016navigating}, culture-dependent subtyping techniques are becoming displaced by culture-independent methods based on whole-genome sequencing (WGS). Secondary analyses, the study of relations and historical relevance of genomes, are now possible on large datasets through WGS \cite{ronholm2016navigating}. Advances in WGS technologies have also enabled the monitoring and sharing of outbreak information in real-time \cite{ronholm2016navigating}.

Subtyping and other analyses software often requires command-line or programming experience. To make these \textit{in-silico} techniques user-friendly for front-line clinicians and laboratories, a variety of web services have been developed in Denmark \cite{joensen2014real}, Canada \cite{whiteside2016superphy} and in collaborations \cite{hasman2015detection}. While useful, argubly \cite{fricke2014bacterial}, the lack of bioinformatic standards and common infrastructure technologies have made it difficult to fully leverage the big-data results from WGS.

Here we present Spfy, a platform for bundling subtyping modules and machine-learning predictions, built using modern containerization of services, task queues for parrelelizing analyses, and exception handling throughout.

>>>>

The surveilance of bacterial pathogens is a routine function of public-health agencies. In \textit{Salmonella enterica} \cite{bell2016recent}, \textit{Escherichia coli} \cite{fratamico2016advances}, and others pathogens \cite{ronholm2016navigating}, culture-dependent subtyping techniques are becoming displaced by culture-independent methods based on whole-genome sequencing (WGS). Secondary analyses, the study of relations and historical relevance of genomes, are now possible on large datasets due to WGS \cite{ronholm2016navigating}. Advances in WGS technologies have also enabled the monitoring and sharing of outbreak information in real-time \cite{ronholm2016navigating}.

Subtyping and other analyses software often require command-line or programming experience. To make such \textit{in-silico} techniques user-friendly for front-line clinicians and laboratories, a variety of web services have been developed in Denmark \cite{joensen2014real}, Canada \cite{whiteside2016superphy}, and in collaborations \cite{hasman2015detection}. While useful, argubly \cite{fricke2014bacterial}, the lack of bioinformatic standards and common infrastructure technologies have made it difficult to fully leverage the big-data results from WGS.

Here we present Spfy, a platform bundling subtyping modules and machine-learning predictions for \textit{E. coli}, built using modern containerization of services, task queues for parrelelizing analyses, and exception handling throughout. Spfy offers serotype predictions, identification of antimicrobial resistance genes through the Comprehensive Antibiotic Resistance Database (CARD) \cite{mcarthur2013comprehensive}, and statisical or machine-learning based comparisons of groups based on user-selected restrictions.
